Prey movement shapes the acquisition of predator expertise in a virtual bi-trophic system

### 2024-09-07 manuscript/manuscript.Rmd
transfered folder to new OS
update files based on GAMM naming changes

```{r summary, cache = TRUE}
# Import top 2 model fits
fit1 <- readRDS(here::here("outputs", "outputs_models", "A2_GAMM-rank.rds"))
fit2 <- readRDS(here::here("outputs", "outputs_models", "A2_GAMM-speed-rank.rds"))

>>>>

```{r summary, cache = TRUE}
# Import top 2 model fits
fit1 <- readRDS(here::here("outputs", "outputs_models", "GAMM-II.rds"))
fit2 <- readRDS(here::here("outputs", "outputs_models", "GAMM-V.rds"))
